### 2023-07-19 Article_PySF.tex
update
update(fix_typo)

{\bf \noindent PROGRAM SUMMARY} \\
\begin{small}
\noindent
{\em Program Title:} PyStructureFactor \\
{\em CPC Library link to program files:} (to be added by Technical Editor) \\
{\em Developer's repository link:} \url{https://github.com/TheStarAlight/PyStructureFactor} \\
{\em Code Ocean capsule:} (to be added by Technical Editor) \\
{\em Licensing provisions:} Apache-2.0 \\
{\em Programming language:} Python 3                                  \\
{\em Supplementary material:}                                 \\
{\em Nature of problem:} The structure factor of a molecule in intense laser fields determines its orientation-dependent tunneling ionization rate, which is crucial for the studies of ultrafast molecular dynamics and its control. However, the strong-field community lacks an open-source code to calculate the molecular structure factor, and can only resort to known results of a few molecules. \\
{\em Solution method:} We develope the \texttt{PyStructureFactor} program with the structure factor of arbitrary molecules calculated using the weak-field asymptotic theory in the integral representation. The underlying electronic structure necessary for the calculation is obtained using the \texttt{PySCF} quantum chemistry package. \\
{\em Restrictions on the Accuracy:} The accuracy of the molecular structure factor calculated by \texttt{PyStructureFactor} is restricted by the level of precision of the electronic structure information extracted from the \texttt{PySCF} package. \\
\cyan{{\em Running time:} The running time depends on the size of the molecule, the basis set of the calculation, the level of precision of the electronic structure calculations, and other parameters passed to the program. The example in Fig.~\ref{fig:code_example} took 1.2 seconds to finish on an AMD Ryzen 9 7950X CPU on the WSL Ubuntu 22.04 LTS.}
\end{small}

@@

Within WFAT, tunneling ionization is investigated in parabolic coordinates. We assume the electric field vector $\bn{F}=F\hat{\bn{z}}$, and define the orientation of the molecule using a set of Euler angles $(\alpha,\beta,\gamma)$ (within the $z$-$y'$-$z''$ convention \cite{madsen_structure_2017}, \cyan{which is shown schematically in Fig.~\ref{fig:EulerAngle}}) representing a rotation $\hat{\bn{R}}$ from the laboratory frame (LF) to the molecular frame (MF). The ionization rate does not depend on $\alpha$ and so we set $\alpha=0$ throughout. The total ionization rate is split into different parabolic channels:
\begin{equation}
    \Gamma(\beta, \gamma)=\sum_\nu \Gamma_\nu(\beta, \gamma),
\end{equation}
where $\Gamma_\nu(\beta, \gamma)$ are partial rates of parabolic quantum number indices
\begin{equation}
    \nu=(n_\xi,m), \quad n_\xi=0,1,2,\cdots, \quad m=0,\pm 1,\pm 2,\cdots
\end{equation}
In the leading-order approximation, the asymptotic expansion of the partial rates for $F\rightarrow 0$ gives
\begin{equation}
    \Gamma_{\nu}(\beta, \gamma) = \abs{G_\nu(\beta, \gamma)}^2 W_{\nu}(F),
\end{equation}
which can be separated into two factors: The structural part $\abs{G_\nu(\beta, \gamma)}^2$ and the field part $W_{\nu}(F)$.
The field factor, $W_{\nu}(F)$, has the form \cite{ammosov_tunnel_1986,delone_tunneling_1998}
\begin{equation}
    W_{\nu}(F) = \frac{\kappa}{2} \left(\frac{4\kappa^2}{F}\right)^{2Z/\kappa-2n_\xi-\abs{m}-1} \ee^{-{2\kappa^3}/{3F}}.
\end{equation}
The structure factor, namely $G_\nu(\beta, \gamma)$, in the integral representation \cyan{of WFAT}, is given as an integral:
\begin{equation}
    G_\nu (\beta,\gamma) = \ee^{-\kappa\mu_z} \int \Omega_\nu^* \left(\hat{\bn{R}}^{-1} \bn{r}\right) \cyan{V}_{\rm{c}}(\bn{r}) \psi_0(\bn{r}) \dd \bn{r},
    \label{eq:StructFactorExp}
\end{equation}
where
\begin{equation}
    \bi{\mu} = \int \psi_0^*(\bn{r}) \bn{r} \psi_0(\bn{r}) \dd \bn{r}
\end{equation}
denotes the orbital dipole moment in the LF with $\mu_z$ its component along the field direction;
$\Omega_\nu$ is a reference function which can be expanded into spherical harmonics:
\begin{equation}
    \Omega_\nu(\bn{r}) = \sum_{l=|m|}^{\infty} \Omega^\nu_{lm}(\bn{r}),
    \label{eq:OmegaExpansion1}
\end{equation}
where
\begin{equation}
    \Omega^\nu_{lm}(\bn{r}) = \sum_{l=|m|}^{\infty} R_l^\nu(r) Y_{lm}(\theta, \phi);
    \label{eq:OmegaExpansion2}
\end{equation}
$\cyan{V}_{\rm{c}}(\bn{r}) = \cyan{V}(\bn{r}) + Z/r$ is the core potential without the Coulomb tail (i.e., $\cyan{V}_{\rm{c}} \rightarrow 0$ as $r\rightarrow \infty$) with $Z$ the asymptotic charge of the parent molecular ion.
The radial part $R_l^\nu$ of the reference function $\Omega_{lm}^\nu$ in Eq.~(\ref{eq:OmegaExpansion2}) reads
\begin{equation}
    R_l^\nu(r)=\omega_l^\nu \ (\kappa r)^l \ \ee^{-\kappa r} \ \rm{M}(l+1-Z/\kappa, 2l+2, 2 \kappa r),
\end{equation}
where $\rm{M}(a, b, x)$ is the confluent hyper-geometric function \cite{olver_nist_2010} and $\omega_l^\nu$ is the normalization coefficient:
\begin{align}
    \omega_l^\nu = & \      (-1)^{l+(\abs{m}-m)/2+1}\ 2^{l+3/2}\ \kappa^{Z/\kappa-(\abs{m}+1)/2-n_\xi} \nonumber \\
                   & \times \sqrt{(2l+1)(l+m)!(l-m)!(\abs{m}+n_\xi)!n_\xi!}\ \frac{l!}{(2l+1)!} \nonumber \\
                   & \times \!\!\!\!\!\! \sum_{k=0}^{\min{(n_\xi,l-\abs{m})}} \!\!\!\!\!\!\!\!\!\! \frac{\Gamma(l+1-Z/\kappa+n\xi-k)}{k!(l-k)!(\abs{m}+k)!(l-\abs{m}-k)!(n_\xi-k)!}.
\end{align}

@@

\begin{table}[tb]
    \small
    \centering
    \begin{tabular}{l p{9cm} l}
        \hline \hline
        Parameter                   & Description                                                                                       & Default\\
        \hline
        \texttt{atom}               & Information of the molecular structure. Refer to Fig.~\ref{fig:code_example} for an example.      & ---\\
        \texttt{unit}               & The unit used for the position coordinates of the atoms in the molecule.
                                      \texttt{'B'} or \texttt{'AU'} indicates Bohr and otherwise Angstr\"om.                            & \texttt{'Angstr\"om'}\\
        \texttt{basis}              & Basis set used for calculation.
                                      Refer to \href{https://pyscf.org/pyscf_api_docs/pyscf.gto.basis.html}{\texttt{pyscf.gto.basis}}
                                      for more information.
                                      An accurate basis set is suggested for optimal convergence.                                       & \texttt{'sto-3g'}\\
        \texttt{charge}             & Charge of the molecule or molecular ion.                                                          & 0 \\
        \texttt{spin}               & Number of spin (i.e., $2S$) of the molecule.                                                      & 0 \\
        \hline \hline
    \end{tabular}
    \caption{Essential input parameters of the \texttt{pyscf.M} method in the \texttt{PyStructureFactor} program.}
    \label{tab:pyscfm_param}
\end{table}

@@

        \texttt{orient\_grid\_size} & Size of the output $(\beta,\gamma)$ grid.

>>>>

{\bf \noindent PROGRAM SUMMARY} \\
\begin{small}
\noindent
{\em Program Title:} PyStructureFactor \\
{\em CPC Library link to program files:} (to be added by Technical Editor) \\
{\em Developer's repository link:} \url{https://github.com/TheStarAlight/PyStructureFactor} \\
{\em Code Ocean capsule:} (to be added by Technical Editor) \\
{\em Licensing provisions:} Apache-2.0 \\
{\em Programming language:} Python 3                                  \\
{\em Supplementary material:}                                 \\
{\em Nature of problem:} The structure factor of a molecule in intense laser fields determines its orientation-dependent tunneling ionization rate, which is crucial for the studies of ultrafast molecular dynamics and its control. However, the strong-field community lacks an open-source code to calculate the molecular structure factor, and can only resort to known results of a few molecules. \\
{\em Solution method:} We developed the \texttt{PyStructureFactor} program with the structure factor of arbitrary molecules calculated using the weak-field asymptotic theory in the integral representation. The underlying electronic structure necessary for the calculation is obtained using the \texttt{PySCF} quantum chemistry package. \\
{\em Restrictions on the Accuracy:} The accuracy of the molecular structure factor calculated by \texttt{PyStructureFactor} is restricted by the level of precision of the electronic structure information extracted from the \texttt{PySCF} package. \\
\cyan{{\em Running time:} The running time depends on the size of the molecule, the basis set of the calculation, the level of precision of the electronic structure calculations, and other parameters passed to the program. The example in Fig.~\ref{fig:code_example} took 1.2 seconds to finish on an AMD Ryzen 9 7950X CPU on the WSL Ubuntu 22.04 LTS.}
\end{small}

@@

Within WFAT, tunneling ionization is investigated in parabolic coordinates. We assume the electric field vector $\bn{F}=F\hat{\bn{z}}$, and define the orientation of the molecule using a set of Euler angles $(\alpha,\beta,\gamma)$ (within the $z$-$y'$-$z''$ convention \cite{madsen_structure_2017}, \cyan{which is shown schematically in Fig.~\ref{fig:EulerAngle}}) representing a rotation $\hat{\bn{R}}$ from the laboratory frame (LF) to the molecular frame (MF). The ionization rate does not depend on $\alpha$ and so we set $\alpha=0$ throughout. The total ionization rate is split into different parabolic channels:
\begin{equation}
    \Gamma(\beta, \gamma)=\sum_\nu \Gamma_\nu(\beta, \gamma),
\end{equation}
where $\Gamma_\nu(\beta, \gamma)$ are partial rates of parabolic quantum number indices
\begin{equation}
    \nu=(n_\xi,m), \quad n_\xi=0,1,2,\cdots, \quad m=0,\pm 1,\pm 2,\cdots
\end{equation}
In the leading-order approximation, the asymptotic expansion of the partial rates for $F\rightarrow 0$ gives
\begin{equation}
    \Gamma_{\nu}(\beta, \gamma) = \abs{G_\nu(\beta, \gamma)}^2 W_{\nu}(F),
\end{equation}
which can be separated into two factors: The structural part $\abs{G_\nu(\beta, \gamma)}^2$ and the field part $W_{\nu}(F)$.
The field factor, $W_{\nu}(F)$, has the form \cite{ammosov_tunnel_1986,delone_tunneling_1998}
\begin{equation}
    W_{\nu}(F) = \frac{\kappa}{2} \left(\frac{4\kappa^2}{F}\right)^{2Z/\kappa-2n_\xi-\abs{m}-1} \ee^{-{2\kappa^3}/{3F}}.
\end{equation}
The structure factor, namely $G_\nu(\beta, \gamma)$, in the integral representation \cyan{of WFAT}, is given as an integral:
\begin{equation}
    G_\nu (\beta,\gamma) = \ee^{-\kappa\mu_z} \int \Omega_\nu^* \left(\hat{\bn{R}}^{-1} \bn{r}\right) \cyan{V}_{\rm{c}}(\bn{r}) \psi_0(\bn{r}) \dd \bn{r},
    \label{eq:StructFactorExp}
\end{equation}
where
\begin{equation}
    \bi{\mu} = \int \psi_0^*(\bn{r}) \bn{r} \psi_0(\bn{r}) \dd \bn{r}
\end{equation}
denotes the orbital dipole moment in the LF with $\mu_z$ its component along the field direction;
$\Omega_\nu$ is a reference function which can be expanded into spherical harmonics:
\begin{equation}
    \Omega_\nu(\bn{r}) = \sum_{l=|m|}^{\infty} \Omega^\nu_{lm}(\bn{r}),
    \label{eq:OmegaExpansion1}
\end{equation}
where
\begin{equation}
    \Omega^\nu_{lm}(\bn{r}) = \sum_{l=|m|}^{\infty} R_l^\nu(r) Y_{lm}(\theta, \phi);
    \label{eq:OmegaExpansion2}
\end{equation}
$\cyan{V}_{\rm{c}}(\bn{r}) = \cyan{V}(\bn{r}) + Z/r$ is the core potential without the Coulomb tail (i.e., $\cyan{V}_{\rm{c}} \rightarrow 0$ as $r\rightarrow \infty$) with $Z$ the asymptotic charge of the parent molecular ion.
The radial part $R_l^\nu$ of the reference function $\Omega_{lm}^\nu$ in Eq.~(\ref{eq:OmegaExpansion2}) reads
\begin{equation}
    R_l^\nu(r)=\omega_l^\nu \ (\kappa r)^l \ \ee^{-\kappa r} \ \rm{M}(l+1-Z/\kappa, 2l+2, 2 \kappa r),
\end{equation}
where $\rm{M}(a, b, x)$ is the confluent hyper-geometric function \cite{olver_nist_2010} and $\omega_l^\nu$ is the normalization coefficient:
\begin{align}
    \omega_l^\nu = & \      (-1)^{l+(\abs{m}-m)/2+1}\ 2^{l+3/2}\ \kappa^{Z/\kappa-(\abs{m}+1)/2-n_\xi} \nonumber \\
                   & \times \sqrt{(2l+1)(l+m)!(l-m)!(\abs{m}+n_\xi)!n_\xi!}\ \frac{l!}{(2l+1)!} \nonumber \\
                   & \times \!\!\!\!\!\! \sum_{k=0}^{\min{(n_\xi,l-\abs{m})}} \!\!\!\!\!\!\!\!\!\! \frac{\Gamma(l+1-Z/\kappa+n_\xi-k)}{k!(l-k)!(\abs{m}+k)!(l-\abs{m}-k)!(n_\xi-k)!}.
\end{align}

@@

\begin{table}[tb]
    \small
    \centering
    \begin{tabular}{l p{9cm} l}
        \hline \hline
        Parameter                   & Description                                                                                       & Default\\
        \hline
        \texttt{atom}               & Information of the molecular structure. Refer to Fig.~\ref{fig:code_example} for an example.      & ---\\
        \texttt{unit}               & The unit used for the position coordinates of the atoms in the molecule.
                                      \texttt{'B'} or \texttt{'AU'} indicates Bohr and otherwise Angstr\"om.                            & \texttt{'Angstr\"om'}\\
        \texttt{basis}              & Basis set used for calculation.
                                      Refer to \href{https://pyscf.org/pyscf_api_docs/pyscf.gto.basis.html}{\texttt{pyscf.gto.basis}}
                                      for more information.
                                      An accurate basis set is suggested for optimal convergence.                                       & \texttt{'sto-3g'}\\
        \texttt{charge}             & Charge of the molecule or molecular ion.                                                          & \texttt{0} \\
        \texttt{spin}               & Number of spin (i.e., $2S$) of the molecule.                                                      & \texttt{0} \\
        \hline \hline
    \end{tabular}
    \caption{Essential input parameters of the \texttt{pyscf.M} method in the \texttt{PyStructureFactor} program.}
    \label{tab:pyscfm_param}
\end{table}

@@

        \texttt{orient\_grid\_size} & Size of the output $(\beta,\gamma)$ grid, \cyan{which defines the orientation of the molecule with respect to the polarization direction of the laser field.}
